Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-02 robdml.tex
tex

>>>>

\subsection{Comparison to State-of-The-Art Defense}
\label{sec:43}

After validating the effectiveness of our proposed method, we conduct
experiments on CUB, CARS and SOP to compare our proposed method
with the state-of-the-art defense methods, \ie, EST~\cite{advrank}
and ACT~\cite{robrank}, as shown in \cref{tab:sota}.

According to the results, EST[$\mathcal{R}$] achieves a relatively high
R@1 when $\eta=8$,
